---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wildwyoung

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

The `wildwyoung` package computes Westfall-Young multiple-hypothesis-adjusted p-values for objects of type `fixest` and `fixest_multi` from the `fixest` package via a wild (cluster) bootstrap. At its current stage, the package is experimental and it is not thoroughly tested.

Because the bootstrap-resampling is based on the [fwildclusterboot](https://github.com/s3alfisc/fwildclusterboot) package, `wildwyoung` is usually really fast. 

The package is complementary to [wildwrolf](https://github.com/s3alfisc/wildrwolf), which implements the multiple hypothesis adjustment method following Romano and Wolf (2005).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("s3alfisc/wyoung")

# from r-universe (windows & mac, compiled R > 4.0 required)
install.packages('wyoung', repos ='https://s3alfisc.r-universe.dev')
```

## Example

<!-- As you can see in the example, there seems to be a bug in `wyoung()` for the pairs bootstrap. -->

```{r, warning=FALSE, message = FALSE}
library(wildwyoung)
library(wildrwolf)
library(fixest)

set.seed(43)

N <- 1000
X1 <- rnorm(N)
X2 <- rnorm(N)
rho <- 0.5
sigma <- matrix(rho, 4, 4); diag(sigma) <- 1
u <- MASS::mvrnorm(n = N, mu = rep(0, 4), Sigma = sigma)
Y1 <- 1 + 1 * X1 + X2 
Y2 <- 1 + 0.01 * X1 + X2
Y3 <- 1 + 0.4 * X1 + X2
Y4 <- 1 + -0.02 * X1 + X2
for(x in 1:4){
  var_char <- paste0("Y", x)
  assign(var_char, get(var_char) + u[,x])
}

# intra-cluster correlation of 0 for all clusters
#numb_clusters <- N / 50
#group_id <- as.character(sample(1:numb_clusters, N, replace = TRUE))

data <- data.frame(Y1 = Y1,
                   Y2 = Y2,
                   Y3 = Y3,
                   Y4 = Y4,
                   X1 = X1,
                   X2 = X2,
                   #group_id = group_id,
                   splitvar = sample(1:2, N, TRUE))

fit <- feols(c(Y1, Y2, Y3, Y4) ~ csw(X1,X2),
             data = data,
             se = "hetero",
             ssc = ssc(cluster.adj = TRUE))

rm(list= ls()[!(ls() %in% c('fit','data'))])

res_wyoung <- wildwyoung::wyoung(
  models = fit,
  param = "X1", 
  B = 9999,
  seed = 23
)
res_rwolf <- wildrwolf::rwolf(
  models = fit,
  param = "X1", 
  B = 9999, 
  seed = 23
)
pvals <- lapply(fit, function(x) pvalue(x)["X1"]) |> unlist()

# Westfall-Young Corrected P-values
summary(res_wyoung)

# Romano-Wolf Corrected P-values
summary(res_rwolf)

# Holm Corrected P-values
p.adjust(pvals, method = "holm") |> round(4)

```

## Performance

The above procedures with `S=8` hypotheses, `N=5000` observations and `k %in% (1,2)` parameters finish each in around 3.5 seconds.

```{r, warning = FALSE, message = FALSE, eval = FALSE}
if(requireNamespace("microbenchmark")){
  
  microbenchmark::microbenchmark(
    "Westfall-Young" = wildwyoung::wyoung(
      models = fit,
      param = "X1", 
      B = 9999,
      seed = 23
    ),
    "Romano-Wolf" = wildrwolf::rwolf(
      models = fit,
      param = "X1", 
      B = 9999, 
      seed = 23
    ), 
    times = 1
  )
 
 # t: seconds
 #           expr      min       lq     mean   median       uq      max neval
 # Westfall-Young 3.625710 3.625710 3.625710 3.625710 3.625710 3.625710     1
 #    Romano-Wolf 3.382969 3.382969 3.382969 3.382969 3.382969 3.382969     1
   
}
```


